MLH1 data report 

### 2018-02-15 1rmd_report.rmd
integrated batch8 female data (with corrections)
fixed some bugs for report file

---
title: "MLH1 data report "
author: "April Peterson"
date: "Feb 6, 2018"
output: github_document
---

@@

# sort your dataframe, by the focal categories
#MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

@@

```{r,  show boxplots, fig.height=5, fig.width=8, echo=FALSE}
qq
high_qual_boxplot
#not sure why order got messed up again...
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16,19, 21) ]
#7: PERC male,   12: #KAZ female! 14:CAST female 16:HMI female,19:SPIC male, 21:SPIC male

>>>>

---
title: "MLH1 data report "
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
---

@@

# sort your dataframe, by the focal categories
MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))
#use the above line for when order is out of wak

@@

```{r,  show boxplots, fig.height=5, fig.width=8, echo=FALSE}
high_qual_boxplot
#not sure why order got messed up again...
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12,14,16,22) ]
#7: PERC male, 12: KAZ female! (14:CAST female, fake data) 16:HMI female
